Language-Based Security for Low-Level MPC

### 2024-05-20 ppdp24/intro.tex
tweak to intro

@@

\paragraph{Hyperproperty formulation.} In Section \ref{section-model} we
develop our formalism for expressing the joint probability mass function of
program variables, and give standard definitions of passive and
malicious real/ideal security in our model. In Section
\ref{section-hyper}, we formulate a variety of familiar information
flow properties in our probabilistic setting, including condition
noninterference, gradual release, and robust declassification, and
consider the relation between these and real/ideal security.  While it
has been previously shown that probabilistic conditional
noninterference is sound for passive security, we formulate new
properties of integrity which, paired with passive security, imply
malicious security (Theorem \ref{theorem-integrity}). We observe
in Section \ref{section-example-bdoz} that authentication mechanisms
such as BDOZ/SPDZ style MACs enforce a strictly weaker property
of ``cheating detection'' (Lemma \ref{lemma-cheating}).

>>>>

Our work provides a complete methodology for end-to-end verification
of MPC protocols via three components:
%
\begin{enumerate}
\item A \textbf{low-level language} for defining MPC primitives
  (\S\ref{section-lang}).
\item A \textbf{fully-automated verification method} for low-level MPC
  primitives in $\mathbb{F}_2$ (\S\ref{section-bruteforce}).
\item A \textbf{partially-automated verification method} for
  high-level MPC protocols, which leverages automated proofs for
  low-level primitives (\S\ref{section-example-gmw}).
\end{enumerate}
%
As part of this methodology, we also develop hyperproperties that
encode MPC security that may be of independent interest. The complete
methodology enables the verification of real-world MPC protocols like
GMW~\cite{goldreich2019play}.

@@

\paragraph{Hyperproperty formulation.} In Section \ref{section-model} we
develop our formalism for expressing the joint probability mass function of
program variables, and give standard definitions of passive and
malicious real/ideal security in our model. In Section
\ref{section-hyper}, we formulate a variety of familiar information
flow properties in our probabilistic setting, including conditional
noninterference, gradual release, and robust declassification, and
consider the relation between these and real/ideal security.  While it
has been previously shown that probabilistic conditional
noninterference is sound for passive security, we formulate new
properties of integrity which, paired with passive security, imply
malicious security (Theorem \ref{theorem-integrity}). We observe
in Section \ref{section-example-bdoz} that authentication mechanisms
such as BDOZ/SPDZ style MACs enforce a strictly weaker property
of ``cheating detection'' (Lemma \ref{lemma-cheating}).
